\section{Minor Bugs}

There were several minor bugs, anomalies and things that did not work, when the sprint was started.
These being minor issues, do not warrant their own sections - however it is worth mentioning some of the problems solved.

\subsection*{Inconsistant UI in \lstinline{ScrollView} of \lstinline{ProfileSelector} activity}

The \lstinline{ScrollView} of the \lstinline{ProfileSelector} activity would overlap the rounded corners of the view when scrolling.
The issue was resolved by overlaying a shape with the corners rounded and a transparent center on the Listview.

\subsection*{Highlighting and Dehighlighting apps when dragging colour}

It was desired to have visual effect for when a colur was dragged over an app.
This achieved by scaling up the app being dragged over by 10\% on \lstinline{DragEvent.ACTION_DRAG_ENTERED} and scaling it down again on \lstinline{DragEvent.ACTION_DRAG_EXITED} and \lstinline{DragEvent.ACTION_DRAG_ENDED}.

\subsection*{Loading Animation on startup}

The previous group expressed that a loading animation when starting Launcher should be available.
This was made by defining a custom animation \lstinline{logoanimation.xml} and launching the animation on startup.

\subsection*{Back button functionality}

While the starting animation plays in \lstinline{LogoActivity} and while on the login screen in \lstinline{AuthenticationActivity}, it should not be possible to use the back button on the tablet.
The issue was resolved by overriding the back button to have no effect in those activities.

\subsection*{Child Mode}

Regardless of being logged in on a child or guardian profile, Launcher would open the \lstinline{ProfileSelector} before opening any app.
It should only open that activity, while in a guardian profile was logged in.
The issue was solved by checking the \lstinline{getRole()} parameter of a profile and then appropiately override the \lstinline{OnClickListener} depending on the role. 

\subsection*{Horizontalize the app}

The Launcher was the only app able to enter portrait mode - all other apps where configured to work in landscape mode.
The \lstinline{AndroidManifest.xml} for the launcher was edited to only allow landscape mode for all activities.

\subsection*{Bugs related to other groups}

There were two bugs found related to other groups than our own.
We did not fix these bugs, but simply reported them to the corresponding groups.

\begin{itemize}
\item The \lstinline{GButton} widget from the GUI group would crash any activity it was used in
\item Danish characters would not decode correctly from the database.
\end{itemize}

There were other, smaller issues, not described in this section.
They were however deemed insignificant.