\section{Sprint End}
At the end of the sprint a sprint review meeting was planned where all groups\frederik{Clarify in preface who all groups are.} and the customers\footnote{Because of the late planning of the meeting only three of the customers was attending.} was attending.

After the meeting we discussed the outcome of the meeting and we all agreed that the meeting was not successful.
The reason for this, in our opinion, was that the meeting was not a sprint review but rather a product presentation.
The meeting was not structured in a way which fulfilled the requirements of a sprint review according to Larman's description of a sprint review in \cite[p. 71]{larmanAgile} is as follows:
\begin{quote}
``At the end of each iteration, there is a review meeting (maximum of four hours)
hosted by the Scrum Master.
The team, Product Owner, and other stakeholders attend.
There is a demo of the product.

Feedback and brainstorming on future directions is encouraged, but no commitments are made during the meeting.
Later at the next Sprint Planning meeting, stakeholders and the team make commitments."
\end{quote}

All stakeholders who Larman lists as people who should be present at the meeting was attending.
All groups presented their work on the project to the customers and the sprint review ended and the  customers left.
Larman encourage that the customers should give feedback to the team at the sprint review meeting.
This was not given since the customers left a demonstration.

As Larman mentions at the end of the quote a Sprint Planning meeting should be held after the sprint review.
Bad communication has led to no Sprint Planning meeting has been arranged.
We were of understanding that it was held on a multi project level but this is not the case.
Therefore we have arranged a meeting with customers to get feedback on our work from this sprint and to present and get new ideas for the second sprint.

