\subsection{Sprint End Organisation}

\begin{frame}{The First Sprint Review}
	This meeting had some fundamental problems:
	\begin{itemize}
		\item No feedback from the clients.
		\item Technical problems with the demonstrations.
		\item Obscure presentations.
		\item Only a few clients were able to attend.
	\end{itemize}
	So, a Sprint End specialist was appointed.
\end{frame}

\begin{frame}{Sprint End Collaboration}
	As the specialist was in this group, we had several tasks in connection with the sprint reviews:
	\begin{itemize}
		\item Instructing the groups on how to present their progress.
		\item Testing that all applications worked together.
		\item Helping groups with last-minute integration problems.
		\item Conduct the client install party.
		\item Host the sprint review meeting.
	\end{itemize}
\end{frame}


\subsection{The Remote Database}

\begin{frame}{Integrating the Remote Database}
	LocalDB had become a component in \textit{Launcher}.\\
	\vspace{\baselineskip}
	Near the end of the fourth sprint, the remote database group were ready to activate synchronisation.\\
	\vspace{\baselineskip}
	We chose to go ahead with this.
\end{frame}

\begin{frame}{Integration Problems}
	The attempt to implement this resulted in several problems:
	\begin{itemize}
		\item Inconsistencies between the two databases.
		\item Inconsistencies between the applications and the modified local database.
		\item The inability of \textit{Pictoseach} to handle large numbers of pictograms.
	\end{itemize}

	\begin{block}{Frederic P. Brooks (1995)}
    	\textit{``All programmers are optimists.''}
   	\end{block}
\end{frame}


\subsection{Multi-Project Management}

\begin{frame}{Roles}
	Roles we used:
	\begin{itemize}
		\item Scrum Master
		\item Client Contact
		\item Sprint End Specialist
	\end{itemize}
	Missing:
	\begin{itemize}
		\item Product Owner
	\end{itemize}
\end{frame}

\begin{frame}{Use of Scrum}
	Scrum only worked to a limited degree.\\
	\vspace{\baselineskip}
	It has been suggested to recommend another method (e.g. UP) to future teams.\\
	\vspace{\baselineskip}
	We however would recommend studying the chosen method extensively, and then implement it right.
\end{frame}

