\subsection{Additional Improvements}

Apart from the improvement described in the above sections, many other improvements are made.
However, most of these do not warrant their own sections.
Therefore, a non-exhaustive list of improvements can be found below:

\subsubsection{Minor bug fixes}
* | | da31f89 (5 days ago) fmikke11@student.aau.dk Fixed nullpointer exception when the fragment was closed before the loading task had finished
| * | | | 64269ef (7 days ago) tonaplo@msn.com Fixed the bug where the progress bar would sometimes keep on spinning after onResume was called.
| * | | cf70e01 (7 days ago) jesper.b.kjaer@gmail.com Fixed problem with the last row in an app container being full.
* | | | 7641e9a (7 days ago) thilemann@gmail.com Fixed error when loading into view first time. Before doInBackground would get an divide-by-zero error.
| * a70262d (13 days ago) fmikke11@student.aau.dk App scaling is now working properly
| * | 91333ed (7 days ago) jesper.b.kjaer@gmail.com The skip animation setting now works (though the logic is reversed).
| | * bd67309 (8 days ago) jesper.b.kjaer@gmail.com Added missing list conversion in updateAppInfoHashMap.

\subsubsection{Minor visual improvements}
* | f5596bb (5 days ago) fmikke11@student.aau.dk Removed padding on 'no apps message text view' in HomeActivity
| | | * | 8cb881b (5 days ago) jesper.b.kjaer@gmail.com Fixed uncapitalized GIRAF tab in settings.
* | 791d914 (5 days ago) thilemann@gmail.com Changed color shown below logo animation when starting launcher
* | | 7eea4d3 (7 days ago) thilemann@gmail.com Added required attributes to elements (width/height)
* | | eee7d65 (7 days ago) thilemann@gmail.com Changed settings activity not found error message to be a bit more verbose
* | | 6381ac1 (7 days ago) thilemann@gmail.com Used dimensions for profile selection from the just added dimens ressource
* | | ae04800 (7 days ago) thilemann@gmail.com Extracted dimensions and added a dimens ressource
| * 7b857ce (13 days ago) fmikke11@student.aau.dk Android apps are now launched properly and an animation has been added when an app is pressed on the homescreen