\launcher: The point of \launcher is to foreclose the citizens from the rest of the tablets functionality.
It should be as simple as possible.
Pernille thinks it is great that one can change the profile both in the \launcher and inside each individual app.
It is nice that it is the same icon to change profiles everywhere.
There are institutions where everyone have their own tablet and others where the citizens must share.
Pernille thinks that \launcher has the nicest design demonstrated today and that the presentation of how it could work has been very good.
Settings should be individual for each citizen.
Pernille thinks it would be realistic to adjust settings inside each app.
Drazenko just wants it to work.
He believes it provides the best overview to adjust the settings inside each app as well.
However, it is very different how technically adept a citizen is.
``Generelt'' is a bad choice of words under the settings for \giraf.
Pernille wants to know why there is an ability to change colours of apps.
Drazenko thinks it is ok, but not an important feature.
It is probably a good idea to discuss with Birken and bostedet what they meant with their colour requirements.
Generally, people are leaning towards adjusting settings inside each individual app.
Drazenko thinks it is a good idea that external apps can be added to \giraf.
It must be possible to lock which applications can be chosen, so a citizen can not just play everything.
Use a different word than ``Android'', since most are used to iPads.
Another idea is to make an ``Import App'' button like when you insert pictures in a Word document.
Keep it clean and simple!
The drawer becomes irrelevant if the colours are not going to be used.
It is not clear what the purpose of the colours is.
Double check that the requirements from the groups from previous years (If you have any problems with requirements, write me a mail!)
The question is whether or not change of colours is still relevant.
An idea could be to remove the possibility of using other applications for a certain period of time, so a citizen can not switch to a different game while working with another.
Drazenko thinks that \launcher is useful and that it should be simple and grant a good overview.
It should be intuitive how the drawer is opened for change of colour.
Go out and test with the users!
Do not say anything, but observe how they are using it. 
That is really good feedback.
Take pictures so you get some great feedback.