\subsection{Minor Bugs}

Several minor bugs, anomalies and things that did not work as expected were found in the beginning of the sprint.
Considering their negligible significance, we will not discuss them in depth, but rather describe each briefly.

\subsubsection{Citizen Mode}
Regardless of whether the currently logged in profile is a citizen or a guardian, \launcher opens the \profileselectionactivity before opening an application.
It should only open that activity while a guardian profile is logged in.
The issue is solved by checking on the \lstinline{getRole()} parameter of a profile, and then appropriately override the \lstinline{OnClickListener} of the \profileselectionactivity, depending on the role. 

\subsubsection{Force Landscape Orientation}
Reports from 2013 developments describes that landscape orientation should be forced in all \giraf applications\cite[p. 33]{2013report}.
Since \launcher is currently able to enter portrait mode, it is corrected by changing \lstinline{AndroidManifest.xml} to only allow landscape orientation for all activities\cite{appManifest}.

\subsubsection{Issues related to other groups}
Two issues caused by other projects are also discovered:

\begin{itemize}
\item The \lstinline{GButton} widget from \textit{GIRAF Components} library crashes any activity that implements it.
\item Danish characters are not encoded correctly in the database.
\end{itemize}

The issues are reported to the groups responsible for these components through the issue tracker.