\subsection{Documenting and commenting the code}
* 7a918e3 (3 days ago) tonaplo@msn.com Completely commented the SettingsListFragment class
* d127f3b (3 days ago) tonaplo@msn.com Completely commented SettingsListAdapter
* 4ab945a (3 days ago) tonaplo@msn.com Added finishing touches to the commenting of the SettingsListItem class and the SettingsUtility class
* 707494a (3 days ago) tonaplo@msn.com Commented the SettingsLauncher class completely
* dfe8a3d (3 days ago) tonaplo@msn.com Completely commented the class SettingsActivity.
* f3cc201 (3 days ago) tonaplo@msn.com Commented the last of GirafFragment
* 7469542 (3 days ago) tonaplo@msn.com Commented the last of AndroidFragment
* 60dc03d (3 days ago) tonaplo@msn.com Commented the class SideBarLayout completely. All layoutcontroller classes have now been commented
* 321314b (3 days ago) tonaplo@msn.com Commented SimulateAnimationDrawable completely
* 2fdb4bb (4 days ago) tonaplo@msn.com Commented the GAppDragger class completely.
* b571175 (4 days ago) tonaplo@msn.com Commented the AppInfo class completely.
* 62d6aa5 (4 days ago) tonaplo@msn.com Commented AppAdapter completely
* d978d98 (4 days ago) tonaplo@msn.com Commented the AppImageView class completely
| * | c27b900 (5 days ago) tonaplo@msn.com commented LoadApplicationTask and renamed its derived class in HomeActivity
| * | 8ce0657 (5 days ago) tonaplo@msn.com Commented LauncerUtility completely.
| * | | | 6abab55 (5 days ago) tonaplo@msn.com Refactored the names of some of the functions in ApplicationControlUtility and commented the entire class

\subsection{Publishing}
* f3c8818 (5 days ago) fmikke11@student.aau.dk Raised the version number of application
* 8777b01 (5 days ago) fmikke11@student.aau.dk Enabled Google Analytics for the launcher apk
| * | | | b740969 (6 days ago) thilemann@gmail.com Changed publisher name to reflect the name of the Google Developers account name used for publishing on Google Play.
* | 03e506b (13 days ago) thilemann@gmail.com Added todo to remember to change the google play publisher constant when giraf is published

\subsection{Saving loaded apps in AppManagementFragment}
| | * e6758cc (5 days ago) fmikke11@student.aau.dk Added comment to GoogleAnalytics xml file. Furhtermore we do no longer load apps each time we change fragment in the apps settings. This is a hugh optimizat
ion.
| | * | | c553b1f (13 days ago) fmikke11@student.aau.dk Preferences are now saved per user
* fcf48a8 (9 days ago) fmikke11@student.aau.dk Settings are now reflected on giraf apps as well when changing profile
| * | cd0ee43 (9 days ago) fmikke11@student.aau.dk Settings are now profile individual, and is reflected on the home screen except giraf apps

\subsection{Minor visual improvements}
* | f5596bb (5 days ago) fmikke11@student.aau.dk Removed padding on 'no apps message text view' in HomeActivity
| | | * | 8cb881b (5 days ago) jesper.b.kjaer@gmail.com Fixed uncapitalized GIRAF tab in settings.
* | 791d914 (5 days ago) thilemann@gmail.com Changed color shown below logo animation when starting launcher
* | | 7eea4d3 (7 days ago) thilemann@gmail.com Added required attributes to elements (width/height)
* | | eee7d65 (7 days ago) thilemann@gmail.com Changed settings activity not found error message to be a bit more verbose
* | | 6381ac1 (7 days ago) thilemann@gmail.com Used dimensions for profile selection from the just added dimens ressource
* | | ae04800 (7 days ago) thilemann@gmail.com Extracted dimensions and added a dimens ressource
| * 7b857ce (13 days ago) fmikke11@student.aau.dk Android apps are now launched properly and an animation has been added when an app is pressed on the homescreen

\subsection{Refactoring (Could be divided into activities)}
* | | 5df867e (5 days ago) thilemann@gmail.com Changed constructors to be chained with private constructor and added documentation to each public constructor.
| | * | | 29b3f39 (5 days ago) thilemann@gmail.com Removed method for setting 'correct' case of application names since it makes more sense that each app is responsible for setting its own name correctly (fo
r example shoud Giraf be written as GIRAF). Also moved getInstalledSettingsApps() method to top of class.
| | * 3c2d0b7 (6 days ago) jesper.b.kjaer@gmail.com Moved Launcher settings' UI strings to settings_strings.xml.
| * | 725dc47 (6 days ago) tonaplo@msn.com attached AppsFragmentInterface on AppContainerFragment instead and moved the methods in GirafFragment and AndroidFragment into AppContainerFragment instead, since t
hey where they same anyways.
| * | 4edd44a (6 days ago) tonaplo@msn.com Moved onViewCreate in AndroidFragment and GirafFragment to AppContainerFragment, since they did the same anyways.
* | | 6d91fd3 (6 days ago) tonaplo@msn.com commented AndroidAppsFragmentInterface and renamed it to AppsFragmentInterface, since both GirafFragment and AndroidFragment implements it. Also made AppContainerFr
agment abstract, since it should always be inherited from and never implemented directly
| * | | | e317dfa (6 days ago) thilemann@gmail.com Refactored listener to be a global variable set from a method called in onCreateView
* | | | | 22dc042 (6 days ago) tonaplo@msn.com Refactored and commented the AndroidFragment class
* | | | 5315298 (6 days ago) thilemann@gmail.com Fixed bug where starting a new activity would preserve the state of the selection in the ListView. Now dont set selected item, but instead notify the adapter
that something has changed. This forces the adapter to redraw its views, and since it is not setting a new selected item, it will draw views in the state prior to starting the activity.
* | | 132ce88 (7 days ago) thilemann@gmail.com Refactored SettingsUtility to exclude methods already available in LauncherUtility. Also added documentation.
* | | 374cc7b (7 days ago) thilemann@gmail.com When adding native android settings to the list, the name is now taken from a string ressource
| * 6a3fe58 (13 days ago) tonaplo@msn.com refactored LauncherUtility so it was more apparent what method to use to call different applications.
* 5cb9846 (12 days ago) thilemann@gmail.com Refactored settings app so SettingsActivity does not know about the adapter nor the listview. The activity now implements the getInstalledGirafApps interface metho
d to return a list containing only valid giraf apps. The listview and adapter is now handled in SettingsListFragment instead. This makes more sense since onCreateView in SettingsListFragment is called before
 onCreate in SettingsActivity.
 | | * d21701c (8 days ago) jesper.b.kjaer@gmail.com Removed uneeded members of AppInfo. Refactored the functions for updating the AppInfo hash map.
 | * | a356d54 (8 days ago) thilemann@gmail.com Changed constructor of SettingsListAdapter to take a ListView as input and added full documentation to SettingsListAdapter.
 * | | 28b33a2 (9 days ago) jesper.b.kjaer@gmail.com Changed some method responsibilities, renamed methods and constants, and added documentation.
 * | 5c590d8 (9 days ago) sthile11@student.aau.dk Completely refactored SettingsListAdapter by implementing the ViewHolder design pattern to minimize calls to findViewById. This also made it possible to replace the methods responsible for setting visibility for each shadow view by a single method just setting the visibility.
 * | 12989ff (9 days ago) thilemann@gmail.com Refactored SettingsActivity so the SettingsListFragment now is responsible for getting the logged in user and then updating this through a interface callback to t
 he activity.
 * | 056508e (9 days ago) thilemann@gmail.com Renamed and added icons for android settings and applications in Settings part of launcher
 * | d66b6a5 (9 days ago) jesper.b.kjaer@gmail.com Removed unused classes: ProfileLauncher and ProfileSelectActivity.
 | | * | | f18363f (8 days ago) jesper.b.kjaer@gmail.com Moved AppInfo hashmap to LauncherUtilities. Fixed check for no available apps.

\subsection{Background loading of data}
| * | | e8aed85 (5 days ago) tonaplo@msn.com made the Animation i MainActivity never cancel, meaning it just gets garbage collected when the activity ends. Also commented the rest of MainActivity
* | | b84f7f1 (5 days ago) tonaplo@msn.com made MainActivity load all the test data in a background thread, so the user doesnt have to wait to a black screen

\subsection{Implement new Profile Selector}
| * | 462e7fb (5 days ago) tonaplo@msn.com made the profilepicture show in SettingsActivity as well and fixed some line breaks.
* | | e396b7a (6 days ago) jesper.b.kjaer@gmail.com Fixed profile picture problem.
| | * | d468059 (origin/testMaster, testMaster) (13 days ago) tonaplo@msn.com Set up Profile Selection to work in Launcher. Still need to add the correct picture to the button though
* | cfda621 (13 days ago) thilemann@gmail.com Removed test string array after profileselector has been implemented
* | 60cbd06 (13 days ago) thilemann@gmail.com Added header to profile selector and refactored the layout a bit
| * 83ecef3 (13 days ago) tonaplo@msn.com profile selection is now done cosmetically. not sure everything works with saving the correct settings to the correct people
| * f0e7bf8 (13 days ago) tonaplo@msn.com profile selection now works as it should in Homeactivity
| * 3d1f227 (13 days ago) tonaplo@msn.com Profile selection works in Homeactivity, but the apps do not change yet
* fa253af (12 days ago) thilemann@gmail.com Changed text of profile selector header

\subsection{Opening the Play Store from SettingsActivity}
| * | 926e5f4 (5 days ago) tonaplo@msn.com commented the rest of AuthenticationActivity and HomeActivity, and made the Play Store open correctly
* | 6b291fa (13 days ago) thilemann@gmail.com Corrected Google Play queries and added them as constants instead of hardcoded values

\subsection{Minor bug fixes}
* | | da31f89 (5 days ago) fmikke11@student.aau.dk Fixed nullpointer exception when the fragment was closed before the loading task had finished
| * | | | 64269ef (7 days ago) tonaplo@msn.com Fixed the bug where the progress bar would sometimes keep on spinning after onResume was called.
| * | | cf70e01 (7 days ago) jesper.b.kjaer@gmail.com Fixed problem with the last row in an app container being full.
* | | | 7641e9a (7 days ago) thilemann@gmail.com Fixed error when loading into view first time. Before doInBackground would get an divide-by-zero error.
| * a70262d (13 days ago) fmikke11@student.aau.dk App scaling is now working properly
| * | 91333ed (7 days ago) jesper.b.kjaer@gmail.com The skip animation setting now works (though the logic is reversed).
| | * bd67309 (8 days ago) jesper.b.kjaer@gmail.com Added missing list conversion in updateAppInfoHashMap.

\subsection{Automatically load newly installed applications in SettingsActivity}
| * | 1530e37 (6 days ago) tonaplo@msn.com Made applications in GirafFragment and AndroidFragment automatically load newly installed applications

\subsection{Android Best Practices}
* | | | 4850aa8 (6 days ago) thilemann@gmail.com Moved Launcher files into its own module as supposed when using Gradle.
| | | * | e9f9693 (8 days ago) fmikke11@student.aau.dk Changed textsizes from type dp to type sp to match android best practices
| | | * | ae78814 (8 days ago) milars11@student.aau.dk Moved all files into an android sub-directory, before merging into launcher.

\subsection{Removed useless widgets}
* | | | | 9761dfa (7 days ago) thilemann@gmail.com Removed the GWidgetConnectivity widget since database syncronization is not currently working and that its dummy implementation has been removed by git GIRA
F_Components project group
| * ad502ea (7 days ago) tonaplo@msn.com Removed the GCalenderWidget and moved some functions into a new UtilityClass

\subsection{Starting settings of other apps from Settings}
* | | c51e137 (7 days ago) thilemann@gmail.com Cleaned file and removed unnecessary intent-filter from SettingsActivity. This activity should not be available through an intent.
* | bd0c2c7 (7 days ago) thilemann@gmail.com When adding an intent by packagename there were no checks that the intent indeed contains the action needed to start the settings of the application. This is now
handled so it is not added to the list if it does not exist.
* | | | 6f19b2e (7 days ago) thilemann@gmail.com Added Sequence (Zebra) to settings
| * | | 0bb96b3 (7 days ago) jesper.b.kjaer@gmail.com Added handling of ActivityNotFound exception in settings.

\subsection{Removing SettingsLib}
| * 5e22ec7 (8 days ago) thilemann@gmail.com Bye bye Settings-Lib, it was nice knowing you... Moved all used files into launcher project and deleted everything else. Settings-Lib is now completely part of la
uncher and no other application is dependent on it. Settings for other applications are opened through intents instead of directly inside Settings App.

\subsection{background worker in Settings}
| * | 63c0ca5 (8 days ago) thilemann@gmail.com Commented remaning parts and simplified logic in which apps are loaded since it can be loaded by either a fragment or intent.
* | | b567fd6 (8 days ago) tonaplo@msn.com Everything regarding adding and removing applications now works, including the ackground workers under any circumstances.
| * | | d6ed500 (8 days ago) tonaplo@msn.com Choosing apps in settings is now completely done.
| * | | | 497235c (8 days ago) tonaplo@msn.com Made marking work with Giraf Apps, still need to make it work with Android Apps.
| * | | c3a5b62 (8 days ago) fmikke11@student.aau.dk Committed the second part of the background worker
| * | | 9724077 (8 days ago) fmikke11@student.aau.dk Committed the first part of the background worker changes
| * | 2fad2e8 (9 days ago) fmikke11@student.aau.dk Added progress bar to the Android application settings fragment

\subsection{Cleaning up after previous groups and IDEs}
* | | 2cca78b (7 days ago) thilemann@gmail.com Removed leftovers from last project groups: srcTest
| * | 0ebbcd5 (8 days ago) thilemann@gmail.com Renamed module 'android' to 'barcodescanner' and changed gradle files accordingly + removed Launcher module and files until whole launcher is added as a module.
| * | 3060f1e (8 days ago) thilemann@gmail.com Deleted unused files that was a leftover from when Eclipse IDE was used.

\subsection{Splitting up LauncherUtility}
* | 3f60829 (8 days ago) tonaplo@msn.com Refactored the last part of LauncherUtility and commented some of the remaining functions.
* | 971f45f (8 days ago) tonaplo@msn.com Refactored GirafFragment to work like Android Fragment and removed some redundant calls to udateAppInfoHashMap
* | ae5936e (8 days ago) tonaplo@msn.com Removed all functions related to getting or checking applications to a new class called ApplicationControlUtility. Also removed two redundant functions.
