Google Analytics is a tool for gathering statistics on the use of mobile applications and websites. 
It is developed to help marketers reach their target groups, by analysing how their applications are used.

Most of the possibilites of Google Analytics are not directly relevant for the \giraf project, however it has a feature which could be of great use.
Google Analytics can automatically record uncaught exceptions that occur on the users' devices.
This is a useful feature for multiple reasons. 
The users may not report an application crash to the developers, which prevents the developers from addressing the underlying issue. 
Furthermore, Google Analytics continuously monitors problems with the applications, even during the eight months each year, where no students are assigned to the project. 
When a new team a students resume the work, they immediately start addressing issues that may have shown up during this period.

A member of this group initially came up with the idea of integrating Google Analytics into the \giraf project.
He was made responsible for instructing groups in setting up the tool and make sure that it was implemented correctly.

%\subsection{Set up}

%Google Analytics is relatively easy to set up, having the following requirements:

%\begin{itemize}
%\item The device must be connected to the Internet.
%\item The Google Analytics SDK must be included in compilation of the application.
%\item An XML file with Google Analytics settings for the specific application must be created and included with the application.
%\item Each activity must have methods for starting and stopping recording of usage statistics. These two methods are implemented in the \lstinline{onCreate()} and \lstinline{onStop()} methods of each activity.
%\end{itemize}
%The XML file should include information such as the \textit{tracking ID}, which allows Google's servers to identify which project the information is related to.

%The responsible member from this group wrote a tutorial, which was distributed to the other groups.

\subsection{Settings for Data Sharing}
When setting up the account at Google Analytics, one is asked to decide whether or not to share the collected analysis data from your applications with other applications.
For this project, we have decided to deactivate all data sharing with external applications, since the ones in this project may contain person sensitive information which we do not by any means want to share with anyone.